\documentclass[doc/report.tex]{subfile}

\begin{document}

\section{Result}

An implementation of a detection and classification has been implemented with
MatLab using the algorithms described in the method section. The effectiveness
of the classifier has been measured using the given measurement set as well as
an unbiased evaluation set. The total number of errors are displayed in table
\ref{tab:meas} for the measurement set and in table \ref{tab:eval} for the
evaluation set. Positive numbers mean the classifier thought there were more
coins of the specified currency than labeled, and vice versa for negative
numbers.

\begin{table}
    \centering
    \begin{tabular}{lrrrrrr}
      nr  & 5c & 10c & 20c & 50c & 1EUR & 2EUR \\\hline
      1772 & 0  & 0   & 0   & 0   & 0   & 0 \\
      1773 & 0  & 0   & 0   & 0   & 0   & 0 \\
      1774 & 0  & 0   & 0   & 0   & 0   & 0 \\
      1775 & 0  & 0   & 0   & 0   & 0   & 0 \\
      1776 & 0  & 0   & 0   & 0   & 0   & 0 \\
      1777 & 0  & 0   & 0   & 0   & 0   & 0 \\
      1778 & 0  & 0   & 0   & 0   & 0   & 0 \\
      1779 & 0  & 0   & -1  & 0   & 0   & 0 \\
      1780 & 0  & 0   & 0   & 0   & 0   & 0 \\
      1781 & 0  & 0   & 0   & 0   & 0   & 0 \\
      1782 & 0  & 0   & 0   & 0   & 0   & 0 \\
      1783 & 0  & 0   & 0   & 0   & 0   & 0 \\
    \end{tabular}
    \caption{All errors for each image of the given measurement set.}
    \label{tab:meas}
\end{table}

\begin{table}
    \centering
    \begin{tabular}{lrrrrrr}
      nr  & 5c & 10c & 20c & 50c & 1EUR & 2EUR \\\hline
      1   & -3 & -1  & 0   & 0   & 0   & 0  \\
      2   & -1 & -1  & 0   & 0   & 0   & 0  \\
      3   & 1  & 0   & 0   & 0   & 0   & -1 \\
      4   & 0  & 0   & 0   & 0   & 0   & 0  \\
    \end{tabular}
    \caption{All errors for each image of the evaluation set.}
    \label{tab:eval}
\end{table}

For the measurement set, there was one misclassified coin out of a total of 76
coins in 12 images. The implementation did not detect a 20c coin on the
checkerboard. For the evaluation set, 6 coins were undetected and 1 coin was
misclassified for a total of 40 coins in four images.

The accuracy was thus roughly 99\% for the measurement set and 82\% for the
evaluation set. However, after inspection it turns out that all undetected
coins were on the checkerboard and the detection ratio was therefore exactly
the same as the ratio of coins laying outside the checkerboard. The one coin
that was misclassified was a 2 Euro coin mistaken for a 10c coin because only
the inner part was segmented.

\end{document}
